The Stakes of Scrying: \texttt{\string.\string^} dotket and the Seer Proposal

### 2024-01-11 mss.tex
Reformat TOC.

%  Make first page footer:
\fancypagestyle{firststyle}{%
\fancyhf{}% Clear header/footer
\fancyhead{}
\fancyfoot[L]{{\footnotesize
              %% We toggle between these:
              Manuscript submitted for review.\\
              % {\it Urbit Systems Technical Journal} I:1 (2024):  1–3. \\
              ~ \\
              Address author correspondence to \patp{rovnys-ricfer}.
              }}
}
%  Arrange subsequent pages:
\fancyhf{}
\fancyhead[LE]{{\urbitfont Urbit Systems Technical Journal}}
\fancyhead[RO]{The Stakes of Scrying with \texttt{\string.\string^} dotket and the Seer Proposal}
\fancyfoot[LE,RO]{\thepage}

@@

%%MANUSCRIPT
\title{The Stakes of Scrying with \texttt{\string.\string^} dotket and the Seer Proposal}
\author{\authorname~\authorpatp \\ \affiliation}
\date{}

@@

\section{How \dotket~Works}

>>>>

%  Make first page footer:
\fancypagestyle{firststyle}{%
\fancyhf{}% Clear header/footer
\fancyhead{}
\fancyfoot[L]{{\footnotesize
              %% We toggle between these:
              Manuscript submitted for review.\\
              % {\it Urbit Systems Technical Journal} I:1 (2024):  1–3. \\
              ~ \\
              Address author correspondence to \patp{rovnys-ricfer}.
              }}
}
%  Arrange subsequent pages:
\fancyhf{}
\fancyhead[LE]{{\urbitfont Urbit Systems Technical Journal}}
\fancyhead[RO]{The Stakes of Scrying:  \texttt{\string.\string^} dotket and the Seer Proposal}
\fancyfoot[LE,RO]{\thepage}

@@

%%MANUSCRIPT
\title{The Stakes of Scrying:  \texttt{\string.\string^} dotket and the Seer Proposal}
\author{\authorname~\authorpatp \\ \affiliation}
\date{}

@@

\section[How dotket Works]{How \dotket~Works}
